Something something values disclosure replication

### 2022-07-12 paper/paper.Qmd
wide table problem solved

library(here)
here()
out_dir = here('out')
```

@@

```{r}
#| label: tbl-bc
#| tbl-cap: "Regression analysis for hypotheses H2 (consumer risk sensitivity) and H3 (disclosure effect)"
bc_tbl = readRDS(here(out_dir, '03_bc_tbl.Rds'))
bc_tbl
```

@@

```{r}
#| label: tbl-shared
#| tbl-cap: "Sequential regression analysis of hypothesis H4 shared values/scientist values effects"
shared_values_tbl = readRDS(here(out_dir, '03_shared_values_tbl.Rds'))
shared_values_tbl
```

@@

```{r}
#| label: tbl-eb
#| tbl-cap: "Regression analysis of H5-consumer, interaction between participant values and consumer risk sensitivity"
readRDS(here(out_dir, '03_eb_tbl.Rds'))
```

@@

```{r}
#| label: tbl-ec
#| tbl-cap: "Regression analysis of H5-transparency, interaction between participant values and transparency penalty"
readRDS(here(out_dir, '03_ec_tbl.Rds'))
```

@@

```{r}
#| label: tbl-sci-part
#| tbl-cap: "Regression analysis of interaction between scientist values and participant values"
readRDS(here(out_dir, '03_sci_part_tbl.Rds'))
```

>>>>

library(gtsummary)
library(kableExtra)
library(here)
here()
out_dir = here('out')

print_tbl = function(x) {
    x |> 
        as_kable_extra(booktabs = TRUE) |> 
        kable_styling(latex_options = c('scale_down'))
}
```

@@

```{r}
#| label: tbl-bc
#| tbl-cap: "Regression analysis for hypotheses H2 (consumer risk sensitivity) and H3 (disclosure effect)"
readRDS(here(out_dir, '03_bc_tbl.Rds')) |> 
    print_tbl()
```

@@

```{r}
#| label: tbl-shared
#| tbl-cap: "Sequential regression analysis of hypothesis H4 shared values/scientist values effects"
readRDS(here(out_dir, '03_shared_values_tbl.Rds')) |> 
    print_tbl()
```

@@

```{r}
#| label: tbl-eb
#| tbl-cap: "Regression analysis of H5-consumer, interaction between participant values and consumer risk sensitivity"
readRDS(here(out_dir, '03_eb_tbl.Rds')) |> 
    print_tbl()
```

@@

```{r}
#| label: tbl-ec
#| tbl-cap: "Regression analysis of H5-transparency, interaction between participant values and transparency penalty"
readRDS(here(out_dir, '03_ec_tbl.Rds')) |> 
    print_tbl()
```

@@

```{r}
#| label: tbl-sci-part
#| tbl-cap: "Regression analysis of interaction between scientist values and participant values"
readRDS(here(out_dir, '03_sci_part_tbl.Rds')) |> 
    print_tbl()
```
